\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-10 fully-abstract-comp/popl2019/paper.tex
Shorten.

%%% Domains
The words on \trgcm{} are capabilities and data (represented by $\ints$).
We assume a finite set of register names $\RegName$ containing at least $\pcreg$, $\rretd$, $\rretc$, $\rstk$, $\rdata$, $\rtmp{1}$, and $\rtmp{2}$, and we define register files as functions from register names to words.
We have complete memories mapping all addresses to words and memory segments mapping some addresses to words (i.e.\ partial functions).
$\trgcm{}$ has two terminated configurations $\halted$ and $\failed$ that respectively signify a successful execution and an execution where something went wrong, e.g.\ an out-of-bounds memory access.
An executable configuration is a register file and memory pair.

@@

\trgcm{}'s instruction set is somewhat basic with the instructions one expects on most low-level machine as well as capability machine specific instructions.
The instructions that can be considered standard are: unconditional and a conditional jump (\texttt{jmp} and \texttt{jnz}), copy between registers (\texttt{move}), instructions that load from memory and store to memory (\texttt{load} and \texttt{store}), and arithmetic operations (\texttt{plus}, \texttt{minus}, and \texttt{lt}).
The simplest of the capability machine specific instructions simply inspect the type of system native tokens or project one of their fields.
These are \texttt{gettype} (for getting the type of a system token) and \texttt{getp}, \texttt{getl}, \texttt{getb}, \texttt{gete}, and \texttt{geta} (for projecting permission, linearity, base, end, and current address(/seal), respectively).
There are two instructions for manipulating the current address(/seal) of a capability(/set of seals): \texttt{cca} changes the current address(/seal) of a capability(/set of seals) by some offset, and \texttt{seta2b} sets the current address(/seal) of a capability(/set of seals) to the base address(/seal).

@@

\trgcm{} also has an instruction that does the inverse of splitting, so a linear capability, or any capability for that matter, that has been split can be restored (\texttt{splice}).
\trgcm{} has instructions for sealing sealables (\texttt{cseal}) and unsealing pairs of sealed capabilities by crossing security boundaries (\texttt{xjmp}, see below).

>>>>

%%% Domains
Words on \trgcm{} are capabilities and data (represented by $\ints$).
We assume a finite set of register names $\RegName$ containing at least $\pcreg$, $\rretd$, $\rretc$, $\rstk$, $\rdata$, $\rtmp{1}$, and $\rtmp{2}$, and we define register files as functions from register names to words.
We have complete memories mapping all addresses to words and memory segments mapping some addresses to words (i.e.\ partial functions).
$\trgcm{}$ has two terminated configurations $\halted$ and $\failed$ that respectively signify a successful execution and an execution where something went wrong, e.g.\ an out-of-bounds memory access.
An executable configuration is a register file and memory pair.

@@

\trgcm{}'s instruction set is somewhat basic with the instructions one expects on most low-level machine as well as capability-related instructions.
The standard instructions are: unconditional and conditional jump (\texttt{jmp} and \texttt{jnz}), copy between registers (\texttt{move}), instructions that load from memory and store to memory (\texttt{load} and \texttt{store}), and arithmetic operations (\texttt{plus}, \texttt{minus}, and \texttt{lt}).
The simplest of the capability instructions simply inspect the properties of capabilities: type (\textt{gettype}), linearity (\texttt{getl}), range (\texttt{getb} and \texttt{gete}), current address or seal (\texttt{geta}) or permission (\texttt{getp}).
The current address (or seal) of a capability (or set of seals) can be shifted by an offset (\texttt{cca}) or set to the base address (\texttt{seta2b}).

@@

The reverse is possible using \texttt{splice}.
Sealables can be sealed using \texttt{cseal} and pairs of sealed capabilities can be unsealed by crossing security boundaries (\texttt{xjmp}, see below).
